---
title: "AS3-2: 股市動態"
author: "第 12 組 "
date: "`r Sys.time()`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

**股票動態**

股票市場是買賣雙方交易公司股票的地方，也是個人和公司投資的最受歡迎的方式之一。現在估計世界股票市場規模達到數兆。紐約證券交易所位於紐約市，是世界上最大的股票市場。 紐約證券交易所約有2,800家上市公司。在這個問題上，我們將看看其中五家公司的每月股價：IB、通用電氣（GE）、寶潔、可口可樂和波音。此問題中使用的數據來自Infochimps。

使用`read.csv()`下載並讀取以下文件：

+ `data/IBMStock.csv`
+ `data/GEStock.csv`
+ `data/ProcterGambleStock.csv`
+ `data/CocaColaStock.csv`
+ `data/BoeingStock.csv` 

分別存入資料框`IBM`、`GE`、`ProcterGamble`、`CocaCola`和`Boeing`，
每個資料框都有兩個變量，描述如下：

+ `Date`：日期
+ `StockPrice`：給定月份公司的平均股價

在這個案例，我們將看看這些公司的股票動態如何隨著時間的推移而發生變化。

<br><hr>
```{r}
IBM = read.csv("data/IBMStock.csv")
GE = read.csv("data/GEStock.csv")
PG = read.csv("data/ProcterGambleStock.csv")
CK = read.csv("data/CocaColaStock.csv")
BS = read.csv("data/BoeingStock.csv")
```

###  Section-1 Summary Statistics

__§ 1.1__ Our five datasets all have the same number of observations. How many observations are there in each data set?
```{r}
IBM$Date = as.Date(IBM$Date,format="%m/%d/%y")
GE$Date = as.Date(GE$Date,format="%m/%d/%y")
PG$Date = as.Date(PG$Date,format="%m/%d/%y")
CK$Date = as.Date(CK$Date,format="%m/%d/%y")
BS$Date = as.Date(BS$Date,format="%m/%d/%y")

str(IBM)
nrow(IBM)
# Ans : 480
```


__§ 1.2__ What is the earliest year in our datasets?
```{r}
min(IBM$Date)
# Ans : 1970
```

__§ 1.3__ What is the latest year in our datasets?
```{r}
max(IBM$Date)
# Ans : 2009
```

__§ 1.4__ What is the mean stock price of IBM over this time period?
```{r}
mean(IBM$StockPrice)
# Ans : 144.375
```

__§ 1.5__ What is the minimum stock price of General Electric (GE) over this time period?
```{r}
min(GE$StockPrice)
# Ans : 9.293636
```

__§ 1.6__ What is the maximum stock price of Coca-Cola over this time period?
```{r}
max(CK$StockPrice)
# Ans : 146.5843
```

__§ 1.7__ What is the median stock price of Boeing over this time period?
```{r}
median(BS$StockPrice)
# Ans : 44.8834
```

__§ 1.8__ What is the standard deviation of the stock price of Procter & Gamble over this time period?
```{r}
sd(PG$StockPrice)
# Ans : 18.19414
```

<br><hr>

###  Section-2 Visualizing Stock Dynamics

__§ 2.1__ Around what year did Coca-Cola has its highest stock price in this time period? Around what year did Coca-Cola has its lowest stock price in this time period?
```{r}
plot(CK$Date,CK$StockPrice,type = "l",main="GGGGG")
abline(v=CK$Date[which.max(CK$StockPrice)],col="green")
abline(v=CK$Date[which.min(CK$StockPrice)],col="red")
# Ans : 1973 1980
#type = "l"為線圖
#abline(v=x)畫出一條通過x的垂直線
```


__§ 2.2__ In March of 2000, the technology bubble burst, and a stock market crash occurred. According to this plot, which company's stock dropped more?
```{r}
plot(CK$Date[121:385],CK$StockPrice[121:385],main="I am almost dead",xlab="Date",ylab="StockPrice",type = "l",col="red",lwd=1,ylim = c(0,210))
lines(PG$Date[121:385],GE$StockPrice[121:385],col="green",lwd=2)
lines(BS$Date[121:385],BS$StockPrice[121:385],col="blue",lwd=1)
lines(GE$Date[121:385],PG$StockPrice[121:385],col="orange",lwd=1)
lines(IBM$Date[121:385],IBM$StockPrice[121:385],col="purple",lwd=1)
abline(v = as.Date("2000-03-01"),lty=2,col="black")
abline(v = as.Date("1983-07-01"),lty=2,col="black")
legend("topleft",legend=c("Coke","P&G","BE","GE","IMB"),col=c("red","green","blue","orange","purple"),lwd=2,cex=0.8)
#lwd 為線的粗細程度
#lyt 為線的類型，1為實線，2-6為虛線(虛的程度不同)
#legend 做出標示
#cex 調整文字大小
# Ans : P&G
```

__§ 2.3__ (a) Around 1983, the stock for one of these companies (Coca-Cola or Procter and Gamble) was going up, while the other was going down. Which one was going up? 
```{r}
# Ans : Going up : Coca-cola / Going down : P&G
```

(b) In the time period shown in the plot, which stock generally has lower values?
```{r}
mean(CK$StockPrice) > mean(PG$StockPrice)
# Ans : P&G
```


<br><hr>

###  Section-3 Visualizing Stock Dynamics 1995-2005

__§ 3.1__ Which stock fell the most right after the technology bubble burst in March 2000?
```{r}
plot(CK$Date[301:432],CK$StockPrice[301:432],main="So Difficult",xlab="Date",ylab="StockPrice",type = "l",col="red",lwd=2,ylim = c(0,210))
lines(PG$Date[301:432],GE$StockPrice[301:432],col="green",lwd=2)
lines(BS$Date[301:432],BS$StockPrice[301:432],col="blue",lwd=1)
lines(GE$Date[301:432],PG$StockPrice[301:432],col="orange",lwd=1)
lines(IBM$Date[301:432],IBM$StockPrice[301:432],col="purple",lwd=1)
abline(v = as.Date("1997-09-01"),lty=2,col="black")
abline(v = as.Date("1997-11-01"),lty=2,col="black")
abline(v = as.Date("2000-03-01"),lty=2,col="black")
abline(v = as.Date("2004-01-01"),lty=2,col="black")
legend("topright",legend=c("Coke","P&G","BE","GE","IMB"),col=c("red","green","blue","orange","purple"),lwd=3,cex=0.9)
# Ans : GE
```

__§ 3.2__ Which stock reaches the highest value in the time period 1995-2005?
```{r}
# Ans : IBM
```

__§ 3.3__ In October of 1997, there was a global stock market crash that was caused by an economic crisis in Asia. Comparing September 1997 to November 1997, which companies saw a decreasing trend in their stock price? (Select all that apply.)
```{r}
# Ans : P&G、Boeing
```

__§ 3.4__ In the last two years of this time period (2004 and 2005) which stock seems to be performing the best, in terms of increasing stock price?
```{r}
# Ans :Boeing
```


<br><hr>


###  Section-4 Monthly Trends

__§ 4.1__ For IBM, compare the monthly averages to the overall average stock price. In which months has IBM historically had a higher stock price (on average)? Select all that apply.
```{r}
tapply(IBM$StockPrice,format(IBM$Date,"%m"),mean) %>% sort(decreasing = TRUE) > mean(IBM$StockPrice)
#一月到五月
```

__§ 4.2__ General Electric and Coca-Cola both have their highest average stock price in the same month. Which month is this?
```{r}
tapply(GE$StockPrice,format(GE$Date,"%m"),mean) %>% sort %>% tail(1)
tapply(CK$StockPrice,format(CK$Date,"%m"),mean) %>% sort %>% tail(1)
# Ans : 四月
```

__§ 4.3__ For the months of December and January, every company's average stock is higher in one month and lower in the other. In which month are the stock prices lower?
```{r}
plot(tapply(GE$StockPrice,format(GE$Date,"%m"),mean))
# Ans : 十二月
```

<br><br><br>

